\section{Introduction}

Hundreds of thousands of malwares are generated daily, and this number continues to grow because of the development of malware obfuscation tools that leverage differing hash values. However, security experts have limited resources. Security experts perform two tasks: categorize malicious code that not been filtered by a hash value, and research obfuscation techniques or malicious behaviors to cope with new malwares and their variants.

Generally, between these two tasks, the first can be handled by machine learning algorithms. It is impossible for security experts to categorize numerous new malitious programs via static or dynamic analysis. Therefore, systems that automatically classify malware have been created. Malware classification models, such as support vector machines, random forests, and deep neural networks (DNN), having static features such as PE structure or API-call-graphs, have been studied \cite{chen2012malware, park2010fast, bai2014malware, yuan2014droid, saxe2015deep}.

If classifier does not quite accurate, or couldn't cope with new malwares, security experts should verify to check whether the machine learning model works well. The verification process requires a system that enables experts to retrieve and compare samples which are similar to the input samples. Therefore, there is an increasing need for a malware retrieval (MR) system that can validate the classification model while helping with the second task of experts: the deep dive.

MR systems semantically retrieve and rank similar malware samples like natural language or image information retrieval systems. Thus, we want to build a MR system to capture the malware’s meaning.

A semantics-aware system is one that has a semantic relationships with malwares. Even if they are structurally different, one can be regarded as a sample having the same meaning if their behaviors coincide. Likewise, if the behavior of malware differs, even if it is structurally nearly the same, the two samples will retain different meanings. In any case, if the semantic differences between the samples can be considered, it is a semantics-aware system.
 
There was an attempt to build a semantics-aware system using traditional semantic-aware features. First, dynamic features represented the behavior of malware, but they had the disadvantage of being difficult to obtain, because they were searched in all behavior cases \cite{jiang2007stealthy, yan2012droidscope, reina2013system}. In a second method, a syntactic feature obtained by static analysis could not represent the meaning of the malware sample \cite{christodorescu2005semantics, zhang2014semantics}. To overcome this, hand-crafted features were used to better detect the common patterns of malicious activity detected by security experts \cite{jang2011bitshred}. However, to create a machine learning model that expresses complex semantic relationships, it is necessary to consider the application of feature expression learning techniques, such as deep learning.
 
Deep learning can hierarchically learn common latent features to represent malware samples that have the same meaning from not only hand-crafted features engineered by security experts, but also non-engineered inputs, such as malware binaries, source code, metadata, resource files, dynamic behavior logs, and screenshots. Therefore, it is possible to learn abundant complex semantic relationships, which is advantageous for generalizing to samples that we have not seen before.


Thus, if there is a good input feature and a deep learning ability to learn latent features, one learn the semantic relationships of malware. In the natural language domain, skip-gram and CBOW are used (e.g., the front-to-back relationship of a sentence) to learn the semantic relationship \cite{mikolov2013efficient}, or by using metrics to stochastically express the co-occurrence based on context \cite{pennington2014glove}.


However, because we do not have sufficient relationships in malwares, we should make model learn semantic relations through supervised learning. Most deep learning-based malware classifiers learn to classify a single label of malware family. In this case, the representation vectors obtained from learning inform only that malwares are similar when distance between those vectors is small and dissimilar when the distance is large. But the distance does not guarantee a difference in meanings.

Given the aforementioned point, how can model learn the semantics of malware? Malware can display multiple malicious acts or attributes. Thus, the semantics of malware can be considered a combination of malicious actions which called semantic components implied by attributes. We refine the malware tags, offering them to deep learning model, which learns the semantics of the malware. During the learning process, the malware's representation vector is trained via a linear combination of the semantic component vectors to have a specific meaning. We train our model with the proposed metric learning method in which the distance between malware samples in the vector space equals the difference in meaning. Thus, we obtained a malware semantic space representing the semantics of malware samples as vectors.

The metric learning method we proposed uses the multi-label centerloss objective function designed by augmenting centerloss \cite{wen2016discriminative}. This loss function causes the malware representation vector to approach its target semantic vector. This can be used with other loss functions as constraints and is easy to implement. Additionally, as with the scoring technique used in the information retrieval task, we assign a weight to a specific semantic component to provide a constraint that plays a bigger role in ranking than in other components.

Also we introduce a flexible MR system that retrieves malwares from semantically similar malware, semantics of malware or those combinations. Then, we check how well the MR system is created through quantitative and qualitative evaluations.

Our main contributions can be summarized as follows.

\begin{itemize}
\item We model the semantics of malwares as vectors and represent the latent features of the malwares as linear combinations of semantic components. We then embed them on the semantics space. We propose a structure of malware classifier based on deep learning to learn the semantic space.
\item We propose a metric learning method based on multi-label centerloss to learn the difference of semantics in the semantic space.
\item We present a flexible MR system that retrieves malware via malware, semantics, and their combination for malware sample vectors in the semantic space, and we evaluate its performance.
\end{itemize}

The composition of our paper is as follows. Background which contains Deep learning, IR, metric learning, and semantic space for natural language is described in Section 2. Section 3 defines the structure and desired properties for the MR system. Section 4 explains the malware semantic space and shows our suggestions for approximate it. Section 5 describes the data set used in the experiment, the neural network hyperparameter settings, and the quantitative and qualitative test results. In Section 6, we discuss related works. In section 7, we discuss future works. In Section 8, we present our conclusion.



\input{background}
\input{malware_ir_system}
\input{semantics_aware_representational_learning}
\input{evaluation}
\input{future_works}
\input{related_works}
\section{Conclusions}

%싱글레이블로 뉴럴넷 적용했는데 엄청 안좋았다. 근데 이그젝틀리 세임이 아니면 검색이 안되더라ㅣ. 그래서 멀티레이블 달고 

We observe that single-label model (baseline1) couldn't cope with malware retrieval task well. 
To solve this problem, we supervised multi-label and use our metric learning method, MCL. 
When using MCL (average) the performance is improved on 2\% for top 1, 4\% for top10, and 11\% for top 100 than single-label model for the same valid set. 
Additionally we verified that our model could learn the semantics of malwares by observing intra-class and inter-class variances and results of other qualitative tests.



%In this paper, we introduced how to make a malware retrieval system using deep learning. In order to make the system have the semantic understanding attribute, we approximate the semantic space using the proposed loss function, multilabel centerloss. Our MR system was queried in three ways: malware samples, semantic components, a combination of malware samples and semantic components. The results of quantitative and qualitative evaluation showed that the proposed method made the system semantic-aware.

\appendix

%\section{Location}
%Note that in the new ACM style, the Appendices come before the References.

\begin{acks}
% TODO: For the submission, don't include acknowledgments since they would most likely deanonymize you.
\end{acks}
